Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-10-23 files/Overview.tex
ssummary

>>>>

\subsection*{500 Word Summary}
This dissertation is a literature study into the comparison of different dimensional linear model. This comparison is an investigation of the validity of lower dimensional models in practical appplications.

This dissertation embarks on a critical examination and comparative analysis of various linear mechanical models, principally assessing their applicability and accuracy in replicating real-world scenarios. The term "validity" in this context refers to how precisely a model, such as the Timoshenko beam theory or the Reissner-Mindlin plate model, emulates more detailed and complex models in practical applications. The methodological approach pivots around modal analysis, which allows model solutions to be represented as a linear combination of eigenvalues and eigenfunctions, facilitating a systematic comparison between different models primarily through their respective eigenvalues and eigenfunctions.

In Chapter 1, the fundamental models under scrutiny are introduced, including the pivotal Timoshenko beam theory. The chapter seeds the research question concerning the efficacy and applicability of simplified models compared to their complex two-dimensional and three-dimensional counterparts, aiming to validate the practical use of simplified models through a systematic comparative approach.

Chapter 2 delves into general vibration problems, building upon referenced scholarly works. It involves exploring the theoretical framework, involving a linear operator "A" and its relationship with the $C_0$-semigroup, to transfigure the general vibration problem into a system of first-order differential equations, which, through semi-group theory, enables the derivation of a unique solution.

Chapter 3 dives into the Finite Element Method (FEM) and its theoretical underpinnings, bifurcating its exploration into two primary results concerning the Galerkin approximation's convergence and eigenvalue and eigenfunction convergence in a one-dimensional vibration problem within the FEM framework. The chapter seamlessly integrates theory and practical applicability, demonstrating how theoretical advancements lead to robust model solutions through innovative approaches.

Chapter 4 spotlights the Timoshenko beam theory, elucidating its application and methodology via modal analysis and hands-on examples. A unique approach to calculating exact eigenvalues and eigenfunctions considering boundary conditions is unveiled, moving away from standard research practices. It blends theoretical discussions with practical examples and culminates by examining a complex model of a cantilever beam with a tip-body and elastic interfaces, demonstrating the Timoshenko beam theory's practical utility.

In Chapter 5, the FEM is applied to two-dimensional and three-dimensional cantilever beams and a cantilever Reissner-Mindlin plate, aiming to derive numerical formulas for the eigenvalues and eigenfunctions of the models, which will be utilized in Chapter 6. The methods engage bi-cubic or tri-cubic basis functions to optimize the convergence rate and minimize computational requirements.

Chapter 6 orchestrates a comprehensive comparison and validation of the models discussed. It methodically outlines comparative analyses of the Timoshenko beam model against two-dimensional and three-dimensional models, examining their eigenvalues and eigenfunctions for validity. The comparisons span different beam and plate configurations, culminating in an analysis that validates the Reissner-Mindlin plate model against a three-dimensional plate model, affirming its reliability in realistic application dimensions.

In essence, this dissertation offers a rigorous, comparative exploration of linear models, primarily the Timoshenko beam theory and Reissner-Mindlin plate model, juxtaposing them against more complex models, and spotlighting their effectiveness and limitations across various practical contexts through detailed theoretical and practical explorations.
